PCA Toolkit

### 2019-10-21 pca-toolkit.Rmd
save

```{r}

```

>>>>

```{r, out.width="70%"}
knitr::include_graphics("figures/us.svg")
```

Matching POPRES populations to 1000G populations    
(do not match maximum p-values < 0.05):

```{r, out.width="90%"}
knitr::include_graphics("figures/ancestry-popres.png")
```

Matching UKBB populations to 1000G populations (20 minutes)  
(do not match maximum p-values < 0.05):

```{r, out.width="98%"}
knitr::include_graphics("figures/ancestry-UKBB.png")
```
